# Introduction {#intro}


The literatures of interest are:

## rtrends

rtrends  bla bla

[`rtrends`](https://cran.r-project.org/web/packages/rtrends/rtrends.pdf) - although it's not clear to me this is doing anything particularly striking.



- [`adjustedcranlogs`](https://github.com/tylermorganwall/adjustedcranlogs). It looks like sub-samples some CRAN packages and takes a certain quantile to subtract the download count. 
- [`packageRank`](https://github.com/lindbrook/packageRank). Also see [intro post](https://blog.r-hub.io/2020/05/11/packagerank-intro/) which is really well written!
- [`cranlogs`](https://github.com/r-hub/cranlogs) - to download the summary download data. 
- [`cran.stats`](https://github.com/arunsrinivasan/cran.stats)
- [`dlstats`](https://github.com/GuangchuangYu/dlstats)
- [`pkgsearch`](https://github.com/r-hub/pkgsearch/)
- [`Visualize.CRAN.Downloads`](https://cran.r-project.org/web/packages/Visualize.CRAN.Downloads/vignettes/Visualize.CRAN.Downloads.html)

## Helpful tips

You can label chapter and section titles using `{#label}` after them, e.g., we can reference Chapter \@ref(intro). If you do not manually label them, there will be automatic labels anyway, e.g., Chapter \@ref(methods).

Figures and tables with captions will be placed in `figure` and `table` environments, respectively.

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig). Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

You can write citations, too. For example, we are using the **bookdown** package [@R-bookdown] in this sample book, which was built on top of R Markdown and **knitr** [@xie2015].
