# Introduction {#intro}

This is the introduction for this project. Before that, I would like to introduce some terms involved in this project.

- R language : R is a language and environment for statistical computing and graphics which can be extended easily via packages and provide an Open Source route to participation in statistical methodology. It is available as Free Software under the term of the Free Software Foundation’s GNU General Public License[@gnu].

- R Studio : It is an integrated development environment (IDE) for R. It includes a console, syntax-highlighting editor that supports direct code execution, as well as tools for plotting, history, debugging and workspace management.

- R Packages : They are collections of functions and data sets developed by the community. They increase the power of R by improving existing base R functionalities, or by adding new ones.

- CRAN : It is a network of ftp and web servers around the world that store identical, up-to-date, versions of code and documentation for R.

- CRAN mirror : It is a website containing differently located servers, which aims to facilitate people from different regions and countries to access CRAN more smoothly and quickly. And each server is called a mirror.

- API : It is the abbreviation of Application Programming Interface, which is a software intermediary that allows two applications to talk to each other. 

## rtrends

And then we come to the related literatures, which are as followed:

- [`rtrends`](https://cran.r-project.org/web/packages/rtrends/rtrends.pdf)
This is a package used for simple analysis of download logs from the CRAN RStudio Mirror, which contains one dataset and five functions. It's mainly functions are:

(1) abstract all CRAN download logs for a specific date
(2) abstract CRAN download logs for a specific package
(3) abstract CRAN download logs for a several package in a range of dates
(4) merge CRAN download logs with county names
(5) provide sample formatted CRAN logs

- [`adjustedcranlogs`](https://github.com/tylermorganwall/adjustedcranlogs). It looks like sub-samples some CRAN packages and takes a certain quantile to subtract the download count. 

- [`packageRank`](https://github.com/lindbrook/packageRank). Also see [intro post](https://blog.r-hub.io/2020/05/11/packagerank-intro/) which is really well written!

- [`cranlogs`](https://github.com/r-hub/cranlogs) - to download the summary download data. 

- [`cran.stats`](https://github.com/arunsrinivasan/cran.stats)

- [`dlstats`](https://github.com/GuangchuangYu/dlstats)

- [`pkgsearch`](https://github.com/r-hub/pkgsearch/)

- [`Visualize.CRAN.Downloads`](https://cran.r-project.org/web/packages/Visualize.CRAN.Downloads/vignettes/Visualize.CRAN.Downloads.html)

## Helpful tips

You can label chapter and section titles using `{#label}` after them, e.g., we can reference Chapter \@ref(intro). If you do not manually label them, there will be automatic labels anyway, e.g., Chapter \@ref(methods).

Figures and tables with captions will be placed in `figure` and `table` environments, respectively.

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig). Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

You can write citations, too. For example, we are using the **bookdown** package [@R-bookdown] in this sample book, which was built on top of R Markdown and **knitr** [@xie2015].
