# Analysis (Methods)

In this project, we construct eight exploratory data analysis : (a) we explore the daily download of all the packages on CRAN; (b) we analysis the daily download trend of R itself and the download distribution of its version; (c) we compare the top 15 downloaded packages on CRAN on 1st Oct. from year 2013 to 2021 to see how the user preference changes; (d) we figure out the relationship between initial release date and the total download count; (e) we compare two closely related packages `fable` and `forecast` to see the difference between their MA (moving average); (f) we study how the number of commits of master (main) branch on Github repository influence the download count; (g) we explore the relationship between the number of updates of packages and its download count; (h) we analyse the name length pattern for both CRAN task view packages and random packages; (i) we explore how the alphabetic order of packages affect the download count and its statistic features (variance, median).

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      cache = FALSE,
                      cache.path = paste0("cache/",
                                          ifelse(knitr::is_html_output(), "html/", "latex/")),
                      fig.path = "figures/",
                      fig.align = "center",
                      message = FALSE,
                      warning = FALSE)
library(tidyverse)
library(cranlogs)
library(lubridate)
library(glue)
library(rvest)

 library(pkgsearch)
 library(jsonlite)
 library(ctv)
 library(lubridate)
 
 library(htmltools)
 library(httpuv)
 library(httr)
 library(kableExtra)
 library(packageRank)
 library(fpp3)
 library(slider)
 library(rvest)
 library(rlist)
 library(plotly)

theme_set(theme_bw(base_size = 14) +
            theme(plot.title.position = "plot"))

# comment out below to include/exclude analysis
child_docs <- c(
                #"02-S01-pkg-downloads.Rmd",
                "02-S01B-R-downloads.Rmd",
                #"02-S02-top15.Rmd",
                "02-S03-release-date.Rmd",
                #"02-S04-similar-release-date.Rmd",
                "02-S05-github-commits.Rmd",
                "02-S06-trending-pkgs.Rmd",
                "02-S07-pkg-name-length.Rmd",
                "02-S08-pkg-name-order.Rmd",
                NULL)
```

```{r child=child_docs}
```
