## Daily top 15 downloaded packages 

In this section, we studied the top 15 downloaded packages from 2013-04-01 to 2021-04-01 to see how user preferences has been changing. The data was obtained from CRAN website [http://cran.rstudio.com/web/packages/packages.rds].

We are supposed to know that some packages are hold by Rstudio, and some are developed by core personnel or personnel closely related to R, or some prolific developers. Naturally, the number of downloads of these packages will probably be higher. On the one hand, the packages developed by these experienced developers may be more mature and perfect, on the other hand, users are more inclined to use the packages from famous authors, which can be regarded as a kind of "good use" guarantee.

However, the existence of these packages will make the results biased. Therefore, in order to explore the packages constructed by non-special creators, we have screened out four types of packages, namely:

- Packages maintained by R studio
- Packages created by authors from R core group
- Packages created by authors from R secondary group
- Packages created by R related authors
- Packages created by top 20 prolific maintainers (This is resourced at @revolutions)

```{r readcran}
url <- "http://cran.rstudio.com/web/packages/packages.rds"
db <- readRDS(url(url)) %>% 
as.data.frame() %>%
  rename(package = Package)

#cran2013_04_01 <- read_csv("data/2013-04-01.csv")
#cran2014_04_01 <- read_csv("data/2014-04-01.csv")
#cran2015_04_01 <- read_csv("data/2015-04-01.csv")
#cran2016_04_01 <- read_csv("data/2016-04-01.csv")
#cran2017_04_01 <- read_csv("data/2017-04-01.csv")
#cran2018_04_01 <- read_csv("data/2018-04-01.csv")
#cran2019_04_01 <- read_csv("data/2019-04-01.csv")
#cran2020_04_01 <- read_csv("data/2020-04-01.csv")
#cran2021_04_01 <- read_csv("data/2021-04-01.csv")

#save(cran2013_04_01, file=here::here("data/cran2013_04_01.rda"))
#save(cran2014_04_01, file=here::here("data/cran2014_04_01.rda"))
#save(cran2015_04_01, file=here::here("data/cran2015_04_01.rda"))
#save(cran2016_04_01, file=here::here("data/cran2016_04_01.rda"))
#save(cran2017_04_01, file=here::here("data/cran2017_04_01.rda"))
#save(cran2018_04_01, file=here::here("data/cran2018_04_01.rda"))
#save(cran2019_04_01, file=here::here("data/cran2019_04_01.rda"))
#save(cran2020_04_01, file=here::here("data/cran2020_04_01.rda"))
#save(cran2021_04_01, file=here::here("data/cran2021_04_01.rda"))

load("data/cran2013_04_01.rda")
load("data/cran2014_04_01.rda")
load("data/cran2015_04_01.rda")
load("data/cran2016_04_01.rda")
load("data/cran2017_04_01.rda")
load("data/cran2018_04_01.rda")
load("data/cran2019_04_01.rda")
load("data/cran2020_04_01.rda")
load("data/cran2021_04_01.rda")

```

```{r filter-list}
# filter the packages maintained by R studio
pkg_rstusio <- db %>%
  filter(grepl('RStudio', Author)) %>%
  select(package) 


# filter the packages whose author is from R core group
pkg_core <- db %>%
  filter(grepl('Douglas Bates|John Chambers|Peter Dalgaard|Robert Gentleman|Kurt Hornik|Ross Ihaka|Tomas Kalibera|Michael Lawrence|Friedrich Leisch|Uwe Ligges|Thomas Lumley|Martin Maechler|Martin Morgan|Paul Murrell|Brian Ripley|Deepayan Sarkar|Duncan Temple Lang|Luke Tierney|Simon Urbanek|Martyn Plummer|', Author)) %>%
  select(package)

# filter the packages whose author is on R secondary group
pkg_secondary <- db %>%
  filter(!grepl('Guido Masarotto|Duncan Murdoch|Henrik Bengtsson|Roger Bivand|Ben Bolker|David Brahm|Vince Carey|Saikat DebRoy|Matt Dowle|Dirk Eddelbuettel|Claus Ekstrom|John Fox|Paul Gilbert|Yu Gong|Gabor Grothendieck|Frank E Harrell Jr|Peter M. Haverty|Torsten Hothorn|Robert King|Kjetil Kjernsmo|Roger Koenker|Philippe Lambert|Jan de Leeuw|Jim Lindsey|Patrick Lindsey|Catherine Loader| Gordon Maclean|Arni Magnusson|John Maindonald|David Meyer|Ei-ji Nakama|Jens Oehlschägel|Steve Oncley|Richard O’Keefe|Hubert Palme|Roger D. Peng|José C. Pinheiro|Tony Plate|Anthony Rossini| Jonathan Rougier|Petr Savicky|Günther Sawitzki|Marc Schwartz|Arun Srinivasan|Detlef Steuer|Bill Simpson|Gordon Smyth|Adrian Trapletti|Terry Therneau|Rolf Turner|Bill Venables|Gregory R. Warnes| Andreas Weingessel|Morten Welinder|James Wettenhall|Simon Wood|and Achim Zeileis', Author)) %>%
  select(package) 


# filter the packages developed by top 20 prolific maintainers
pkg_20maintainer <- db %>% 
  filter(stringr::str_detect(Author, 'Hadley Wickham|Yihui Xie|Dirk Eddelbuettel|Jeroen Ooms|Achim Zeileis|Scott Chamberlain|Gabor Csardi|Jeroen Ooms|ORPHANED|Thomas J. Leeper|Bob Rudis|Henrik Bengtsson|Kurt Hornik|Oliver Keyes|Martin Maechler|Richard Cotton|Robin K. S. Hankin|Simon Urbanek|Kirill Muller|Torsten Hothorn|Paul Gilbert') )%>%
  select(package) 


# filter the packages developed by other R studio related authors
pkg_r_related <- db %>%
  filter(stringr::str_detect(Author, 'Hadley Wickham|Yihui Xie|Gabor Csardi|Winston Chang|Andrie de Vries|Alison Presmanes Hill|Mara Averick|Cole Arendt|Daniel Falbel|Garrick Aden-Buie|Garrett Grolemund|Gary|Joe Cheng|Jennifer (Jenny) Bryan|Jim Hester|J.J. Allaire|Jonathan|Joshua Spiewak|Dan Buch|Richard Iannone|Ralf Stubner|Tyler Finethy|Melissa Barca|Kevin Ushey|Javier Luraschi|Karl Feinauer|Charles Teague|Maria Semple|adamconroy|Ricardo Andrade|Steve Nolen|Randy Lai|Jeffrey Horner|Jan Marvin Garbuszus|Justace Clutter|Josh Paulson|Mike Bessuille|Jeffrey Arnold|Paul Kaefer|Jim Hester|Dirk Schumacher|
Philipp A.|Fabian Mundt|Fabian Mundt|boB Rudis|Asher|Henrik Bengtsson|James Lamb|rich-rstudio|Andrie de Vries|Iñaki Ucar|Mark Brown|Hiroaki Yutani|Dean Attali|Matthias Mailänder|Bruno Tremblay|Ian|John Blischak|Chris von Csefalvay|Jeroen Ooms|
Daniel Gromer|Kirill Müller|Jan Gleixner|Alexander Grueneberg|Darío Hereñú|Aron Atkins|harupiko|Barret Schloerke|James Arnold|Giuseppe Casalicchio|Fredric Johansson|Curtis Kephart|reudismam|Jeff Allen|Yuri Niyazov|Sean Kross|Carl A. B. Pearson|
Peter Glerup Ericson|Diomidis Spinellis|Paul Menzel|Lincoln Mullen|Colin Gillespie|Masafumi Okada|Øystein Sørensen|Matthew Grogan|Scott Kostyshak|Marcus Kinsella|rhinopotamus|Daiki Katsuragawa|Michael Steinbaugh|Jari Karppinen|Roy Storey|Kristofer Rye|Erin|Ben Torvaney|Pol Mesalles|Sainath Adapa|Vladimir Panfilov|Christian Brueffer|Julien Barnier|') )%>%
  select(package) 

```

```{r filter-function}
# function used to do filtering
filter_list <- function(pkg){
  
  pkg <- pkg %>%
     filter(!(package %in% pkg_20maintainer$package)) %>%
     filter(!(package %in% pkg_secondary$package)) %>%
     filter(!(package %in% pkg_rstusio$package)) %>%
     filter(!(package %in% pkg_core$package)) %>%
     filter(!(package %in% pkg_r_related$package))
  
  return(pkg)
}
```


```{r filterlist}
# exclude the packages in the above three lists
cran2013_04_01_new <- filter_list(cran2013_04_01)
cran2014_04_01_new <- filter_list(cran2014_04_01)
cran2015_04_01_new <- filter_list(cran2015_04_01)
cran2016_04_01_new <- filter_list(cran2016_04_01)
cran2017_04_01_new <- filter_list(cran2017_04_01)
cran2018_04_01_new <- filter_list(cran2018_04_01)
cran2019_04_01_new <- filter_list(cran2019_04_01)
cran2020_04_01_new <- filter_list(cran2020_04_01)
cran2021_04_01_new <- filter_list(cran2021_04_01)
```


```{r crantop15-1319}
# find the top 30 downloaded packages on 04.01 from 2013 to 2021
cran2013_0401 <- cran2013_04_01_new %>%
  drop_na() %>%
  dplyr::count(package) %>%
  arrange(desc(n)) %>%
  head(15) %>%
  select(package)
  
#cran2013_1001$package <- as.vector(cran2013_1001$package) #get rid of factors

#cran2013_1001$package = factor(cran2013_1001$package,cran2013_1001$package)

cran2014_0401 <- cran2014_04_01_new %>%
  drop_na() %>%
  dplyr::count(package) %>%
  arrange(desc(n)) %>%
  head(15) %>%
  select(package)

cran2015_0401 <- cran2015_04_01_new %>%
  drop_na() %>%
  dplyr::count(package) %>%
  arrange(desc(n)) %>%
  head(15) %>%
  select(package)

cran2016_0401 <- cran2016_04_01_new %>%
  drop_na() %>%
  dplyr::count(package) %>%
  arrange(desc(n)) %>%
  head(15) %>%
  select(package)

cran2017_0401 <- cran2017_04_01_new %>%
  drop_na() %>%
  dplyr::count(package) %>%
  arrange(desc(n)) %>%
  head(15) %>%
  select(package)

cran2018_0401 <- cran2018_04_01_new %>%
  drop_na() %>%
  dplyr::count(package) %>%
  arrange(desc(n)) %>%
  head(15) %>%
  select(package)

cran2019_0401 <- cran2019_04_01_new %>%
  drop_na() %>%
  dplyr::count(package) %>%
  arrange(desc(n)) %>%
  head(15) %>%
  select(package)

cran2020_0401 <- cran2020_04_01_new %>%
  drop_na() %>%
  dplyr::count(package) %>%
  arrange(desc(n)) %>%
  head(15) %>%
  select(package)

cran2021_0401 <- cran2021_04_01_new %>%
  drop_na() %>%
  dplyr::count(package) %>%
  arrange(desc(n)) %>%
  head(15) %>%
  select(package)

```


```{r antijoin-1319}
# find out the new top 15 packages added each year
a <- anti_join(cran2014_0401,cran2013_0401) 
b <- anti_join(cran2015_0401,cran2014_0401) 
c <- anti_join(cran2016_0401,cran2015_0401) 
d <- anti_join(cran2017_0401,cran2016_0401) 
e <- anti_join(cran2018_0401,cran2017_0401) 
f <- anti_join(cran2019_0401,cran2018_0401) 
g <- anti_join(cran2020_0401,cran2019_0401) 
h <- anti_join(cran2021_0401,cran2020_0401) 

# function used to combine data with different length 
cbind_dif <- function(x = list()){
    # Find max length
    max_length <- max(unlist(lapply(x, length)))

    # Set length of each vector as
    res <- lapply(x, function(x){
        length(x) <- max_length
        return(x)
    })

    return(as.data.frame(res))
}

pkg_change <- cbind_dif(list(package14_13 = a$package, package15_14 = b$package, package16_15 = c$package, package17_16 = d$package, package18_17 = e$package, package19_18 = f$package,package20_19 = g$package,package21_20 = h$package))

pkg_change[is.na(pkg_change)] = "-"
```

```{r semijoin-1319}
a1 <- semi_join(cran2014_0401,cran2013_0401)  
b1 <- semi_join(cran2015_0401,cran2014_0401) 
c1 <- semi_join(cran2016_0401,cran2015_0401) 
d1 <- semi_join(cran2017_0401,cran2016_0401) 
e1 <- semi_join(cran2018_0401,cran2017_0401) 
f1 <- semi_join(cran2019_0401,cran2018_0401) 
g1 <- semi_join(cran2020_0401,cran2019_0401) 
h1 <- semi_join(cran2021_0401,cran2020_0401) 

pkg_remain <- cbind_dif(list(package14_13 = a1$package, package15_14 = b1$package, package16_15 = c1$package, package17_16 = d1$package, package18_17 = e1$package, package19_18 = f1$package,package20_19 = g1$package,package21_20 = h1$package))

pkg_remain[is.na(pkg_remain)] = "-"
```

And after that, we generated the lorenz curve here again in Figure \@ref(fig:lorenz-filter), it can be observed that the distribution of packages in each download group is quite equal now and the Gini value decreases a lot as well, for the 'extreme effect' brought by highly-downloaded packages has disappeared. Thus, the user preferences could be shown more clearly. But as after filtering, the number of remaining packages is only 58, which is a too small-sized sample to construct representative conclusions, we would still focus on all the packages on CRAN in our later analysis.


(ref:lorenz-filter) Percentiles of the download count against cumulative download count of packages after filtering four types of popular and highly-downloaded packages.

```{r lorenz-filter, fig.cap="(ref:lorenz-filter)"}
cran_names_download_new <- filter_list(cran_names_download)

ggplot(cran_names_download_new, aes(total)) +
stat_lorenz() +
geom_abline(linetype = "dashed") +
annotate_ineq(cran_names_download_new$total)+
theme_bw()+
  labs(
    y = "Cumulative share of download count",
    x = "Download quantile",
    title = "The number of packages occupied by each group",
    subtitle = "based on download count quantile after filtering"
  ) +
  theme(panel.grid.major = element_blank()) +
  theme(
  axis.text=element_text(size=10),
  axis.title=element_text(size=12,face="bold"),
  plot.title = element_text(h = 0.5),
  plot.subtitle = element_text(h = 0.5)
  )
```

```{block, type="discovery", echo = TRUE}
**Finding 1**: The topic of newly added packages each year come from quite different areas. 
```

Table \@ref(tab:changed-top15pkg) shows the packages that newly come up to the top 15 list each year, from which we can know how the user preference has changed year by year, compared with the previous year. To be more specific :

- For 2014, `ncdf` ranks first, which is used to provide an interface to netCDF format data. 
- For 2015, the first downloaded is `XLConnectJars` on JAVA dependency. 
- For 2016, the first one is `reports` for standardising the output of R. 
- For 2017, `lava.tobit` aims to help with estimation and simulation of latent variable models.
- For 2018, the ranking-first `ReportsRs` is for creating Microsoft Word and Powerpoint documents. 
- For 2019, `CALIBERrfimpute` is used to impute missing values in analysis datasets using full conditional specifications. 
- For 2020, `SparkR` is similar to `dplyr` but for large datasets. 
- For 2021, `heatmap.plus` is an extension of `heatmap()` function.


```{r changed-top15pkg}
pkg_change %>%
  kable(caption = "Changed top 15 downloaded packages from 2013 to 2019") %>%
  kable_styling(bootstrap_options = c("hover", "striped")) %>%
  scroll_box(width = "100%", height = "400px")

```

```{block, type="discovery", echo = TRUE}
**Finding 2**: The topic of packages changes least between 2017 and 2019. And the most popular filed is about JAVA dependency.
```

Table \@ref(tab:unchanged-top15pkg) shows the packages that remain unchanged each year compared with the previous year, from which we can know which packages are relatively stable in popularity.

To be more specific, packages like `XLConnectJars`, `DMwR`, `KoNLP`, and `gWidgets` are relatively popular through years from 2014 to 2021. And they are used for providing JAVA dependency, data mining, linguistic research and providing API for building toolkit-independent, interactive GUIs.

```{r  unchanged-top15pkg}
pkg_remain %>%
  kable(caption = "Unchanged top 15 downloaded packages from 2013 to 2019") %>%
  kable_styling(bootstrap_options = c("hover", "striped")) %>%
  scroll_box(width = "100%", height = "400px")
```

Let's take a look at the trending packages. Trending packages are ones that are downloaded at least 1000 times last week, which have increased significantly compared to the average weekly downloads in the previous 24 weeks[@r-hub]. That is to say, they are packages with high download volume in a recent short time. Through their topic, we can know what areas of packages people are concerned about recently.

```{block, type="discovery", echo = TRUE}
**Finding 3**: The most popular topic of trending packages is for Time series analysis.
```

```{r taskview-function}
# to get all the topic names from CRAN task view
library(ctv)
task_topic <- available.views(repos = "https://cran.csiro.au/")

topic_name <- task_topic[[1]]$name
x <- lapply(1:length(task_topic),function(i) { topic_name[i] <- task_topic[[i]]$name})

task_topic_all <- list.rbind(x) %>%
  as.data.frame()

colnames(task_topic_all)[1] <- 'topic'


# to get all the packages from CRAN task view along with their topics
pkg_taskview_total = data.frame()

for (i in c(1:length(task_topic_all$topic))) {
  
    topic_pkg <- ctv:::.get_pkgs_from_ctv_or_repos(paste0(task_topic_all$topic[i]), 
                                              repos = "http://cran.rstudio.com/")[[1]]


   df  <- data.frame(matrix(unlist(topic_pkg), nrow=length(topic_pkg), byrow=TRUE),stringsAsFactors=FALSE) %>%
     mutate(topic = paste0(task_topic_all$topic[i]))
   
   colnames(df)[1] <-'packages'
  
   pkg_taskview_total <- rbind(pkg_taskview_total,df)
  
}

colnames(pkg_taskview_total)[1] <- 'package'

# to figure out the classification of packages according to CRAN task view
# plyr::match_df(pkg_taskview_total,c,on = "package")

```

Table \@ref(tab:trending-topic) shows the first 15 trending packages along with their topics.

```{r trending-topic}
# read trending packages recently
pkg_trending <- cran_trending()

pkg_trending_new <- pkg_trending %>%
  select(-score)

pkg_trending_compare <- plyr::match_df(pkg_taskview_total,pkg_trending_new,on = "package") %>%
  group_by(topic)

pkg_trending_compare %>%
  head(15) %>%
  kable(caption = "trending packages with topics") %>%
  kable_styling(bootstrap_options = c("hover", "striped"))
```

```{r trendingcount}
pkg_trendcom_count <- pkg_trending_compare %>%
  dplyr::count(topic) %>%
  arrange(desc(n))
```

And Table \@ref(tab:trending-count) shows the first 10 topics for trending packages. The most popular topic is `r pkg_trendcom_count$topic[1]`, followed by `r pkg_trendcom_count$topic[2]` and `r pkg_trendcom_count$topic[3]`. This is easy to understand, because the number of users from different fields is different, so there are also differences in the number of packages used in different topics. And it seems that `r pkg_trendcom_count$topic[1]` is quite a hit recently.

```{r trending-count}
pkg_trendcom_count %>%
  head(10) %>%
  kable(caption = "Topics of trending packages") %>%
  kable_styling(bootstrap_options = c("hover", "striped"))
```

So, apart from the topic of the package itself, what other factors will affect its download volume? With this problem in mind, we mainly explored the relationship between the total number of download counts of packages in the past half a year and the earliest release date, the number of updates, the number of commits on GitHub repositories, the length of the name and the alphabetical order of the first letter of the name in the next following sections.
