# Results

## Daily downloads of R-packages

```{r vars-pkg-downloads, cache = TRUE}
dd_start <- "2012-10-01" #from the openning of cran
dd_end <- Sys.Date() - 2

is_weekend <- function(date) {
  weekdays(date) %in% c("Saturday", "Sunday")
}

total_downloads <- cran_downloads(from = dd_start, to = dd_end) %>% 
  mutate(year = year(date),
         day = yday(date),
         weekend = is_weekend(date)) 
```


```{block, type="discovery", echo = TRUE}
**Finding 1**: There was unusual download activities in one day of 2014 and 2018. 
```

In this first section, we studied the daily downloads of CRAN R-packages from `r dd_start` to `r dd_end`. The data was obtained from the `cranlogs` package[@cranlogs], which includes a summary of the download logs via the RStudio CRAN mirror. The daily download data for CRAN R-packages are available from 1st October 2012. Examination of this data showed two unusual observations in 2014 and 2018 as shown in Figure \@ref(fig:unusual-spikes). The one happening in 2014 was on 2014-11-17, Monday, while the other one happening in 2018 was on 2018-10-21, Sunday.


(ref:unusual-spikes) Unusual download spikes in 2014 and 2018. 

```{r unusual-spikes, fig.cap="(ref:unusual-spikes)",cache = TRUE}
plot_daily <- total_downloads %>% 
  group_by(year) %>% 
  mutate(max_count = max(count)) %>% 
  ungroup() %>% 
  filter(year %in% c(2014, 2018)) %>% 
  ggplot(aes(x = day, y = count/1e6)) +
  geom_area(aes(y = weekend * max_count/1e6),
            fill="#e3e3e3")+
  geom_line() +
  labs(x = "Day",
       y = 'Download count (in millions)',
       title = "Daily downloads for 2014 and 2018") +
  facet_grid(facets = year ~ ., 
             scales = "free_y") +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
  plot.title = element_text(h = 0.5))

plot_daily
```


```{r unusual-spike}
#daily_download_20141117 <- read_csv("data/2014-11-17.csv")
#daily_download_20181021 <- read_csv("data/2018-10-21.csv")

#save(daily_download_20141117, file=here::here("data/daily_download_20141117.rda"))
#save(daily_download_20181021, file=here::here("data/daily_download_20181021.rda"))

load("data/daily_download_20141117.rda")
load("data/daily_download_20181021.rda")
```

When having a closer look into those two spikes, we firstly focused on the one on 2014-11-17. From Table \@ref(tab:spike14count), we could see that the downloads of top downloaded R-packages on this day differs little, indicating this spike is not due to a certain package.

```{r spike14count}
## for 2014-11-17
daily_download_20141117 %>%
  group_by(package) %>%
  count() %>%
  arrange(desc(n))%>% 
  head(10) %>%
  kable(caption = "The total downloads of each R-package on 2014-11-17") %>%
  kable_styling(full_width = FALSE)
```

Table \@ref(tab:spike14country) shows the downloads from different countries on 2014-11-17. It is obvious that `Indonesia` obtains much more downloads than any others.

```{r spike14country}
daily_download_20141117 %>%
  group_by(country) %>%
  count() %>%
  arrange(desc(n))%>% 
  head(10) %>%
  kable(caption = "The countries downloading from CRAN on 2014-11-17") %>%
  kable_styling(full_width = FALSE) #downloads from Indonesia is much more than any others
```

Furthermore, we also checked IP addresses, displayed in Table \@ref(tab:spike14ip). Downloads from `ip3758` is much higher than others. So, it seems that most of the downloads are owing to one certain IP for the unusual spike in 2014. 

```{r spike14ip}
daily_download_20141117 %>%
  group_by(ip_id) %>%
  count() %>%
  arrange(desc(n))%>% 
  head(10) %>%
  kable(caption = "The IP addresses downloading from CRAN on 2014-11-17") %>%
  kable_styling(full_width = FALSE) #downloads from ip3758 is much higher than others

```

Next, we turned to the unusual spike in 2018. Table \@ref(tab:spike18count) shows the downloads from `tidyverse` is much higher than others, with nearly three orders of magnitude. 

```{r spike18count}
## for 2018-10-21
daily_download_20181021 %>%
  group_by(package) %>%
  count() %>%
  arrange(desc(n))%>% 
  head(10) %>%
  kable(caption = "The total downloads of each R-package on 2018-10-21") %>%
  kable_styling(full_width = FALSE) 

```

As for country, from Table \@ref(tab:spike18country), we could know that `US` occupies the most part of downloads on that day.

```{r spike18country}
daily_download_20181021 %>%
  group_by(country) %>%
  count() %>%
  arrange(desc(n))%>% 
  head(10) %>%
  kable(caption = "The countries downloading from CRAN on 2018-10-21") %>%
  kable_styling(full_width = FALSE) 

```

Finally, the most interesting finding is on IP address, displayed in Table \@ref(tab:spike18ip). Several consecutive IPs have highly distinguished downloads. It seems that they are probably from the same individual, or caused by a server test issue, in such a short period of time.

```{r spike18ip}
daily_download_20181021 %>%
  group_by(ip_id) %>%
  count() %>%
  arrange(desc(n))%>% 
  head(10) %>%
  kable(caption = "The IP addresses downloading from CRAN on 2018-10-21") %>%
  kable_styling(full_width = FALSE) #several ip has highly distiguished downloads and they are contiguous. It seems that they are from same person, and it is also probably that it's a server issue.

```

To sum up, we found that these two unusual spikes have one thing in common, that is, most of the downloads came from a specific country. The difference is that in 2014, a large number of downloads came from several different R-packages, while in 2018, they came from only one package `tidyverse`. In addition, in 2014, a large quantities of downloads came from one IP, while in 2018, they came from several consecutive IPs, At this point, it is guessed that they should come from the same individual, and it is very likely due to sever test issue, for it may be not necessary or reasonable for an individual to generate such a large amount downloads in one day.


```{block, type="discovery", echo = TRUE}
**Finding 2**: There are increasing numbers of downloads over time, which can attests the growing number of R users. 
```

Figure \@ref(fig:download-over-time) shows the download trend of all R-packages on CRAN over a period pf time from `r dd_start` to `r dd_end`, after fixing the unusual spikes mentioned above. There is an upward trend, with an increasing variance in download counts.

(ref:download-over-time) The download trend of all R-packages on CRAN from `r dd_start` to `r dd_end`. 

```{r download-over-time, fig.cap="(ref:download-over-time)"}
total_downloads_fix <- total_downloads %>% 
  mutate(count = ifelse(count > 3e6 & year==2014 | count > 10e6 & year==2018, 
                        NA, count)) %>% #remove the unusual observations in 2014 and 2018
  group_by(year) %>% 
  mutate(max_count = max(count, na.rm = TRUE)) %>% 
  ungroup()

total_downloads_fix %>% 
  ggplot(aes(date, count/1e6)) +
  geom_line(colour="gray") +
  labs(x = "Date", y = "Download count (in millions)",title = "Daily download count of all of R-packages")
```

```{block, type="discovery", echo = TRUE}
**Finding 3**: Weekends have a lower downloads than weekdays.
```

To have a closer look at the weekly pattern, figure \@ref(fig:total-trend) shows the daily downloads of all CRAN R-packages via the RStudio mirror, with the grey areas highlighting the weekend. 

To be more specific, except for 2012 and 2013, the patterns of other years are very similar, with a strong weekly seasonality. To be more detailed, in 2012, the download logs showed an overall upward trend, which also reflected more and more users there after release of CRAN. In the following years, there is no obvious trend in download volume, but a strong seasonality, which indicates that in a week, the total downloads always increases first then decreases, and reaches the lowest on weekends. Although the pattern of 2013 is more volatile, it still conforms to that. We suppose that is because CRAN was only open for a short period of time in 2013, so the amount of download data is not adequate to show the weekly pattern very clearly. After 2016, the pattern of each year is quite consistent, for the total downloads have been increasing year by year. Back to weekly seasonality, people are more likely to download packages during weekdays, and rest on weekends. So, the trough of download curve always occurs on weekends. In addition, the lowest downloads across the year are always happening at the end of December or the beginning of January, probably due to the Christmas and New Year's holidays. Meanwhile, the downloads are on the rise from August to October, and from February to April, which covers the beginning of semesters for many universities around the world, a time when related students tend to download CRAN R-packages very often. 

(ref:total-trend) The total downloads for all of R-packages on CRAN would decrease on weekends and increase during weekdays.

```{r total-trend, fig.cap="(ref:total-trend)", fig.height = 12,cache = TRUE}

plot_daily_fix <- plot_daily +
  labs(title = "Total number of downloads for R-package on CRAN",
       subtitle = glue("from {dd_start} to {dd_end}")) 
  

plot_daily_fix %+%
   total_downloads_fix
```

As there are many fluctuations in daily download pattern, which is due to calendar effect and test server issue of CRAN mirror, an STL decomposition model explained in @stl, was applied, to smooth the curve for all of the R-packages in Figure \@ref(fig:pkg-stl). 

(ref:pkg-stl) The total downloads of all R-packages on CRAN after smoothing.

```{r pkg-stl, fig.cap="(ref:pkg-stl)"}
# try to use stl model to smooth the curve
total_download_tsble <- total_downloads_fix %>%
  as_tsibble(index = date)

total_download_tsble[is.na(total_download_tsble)] <- 0

pkg_stl <- total_download_tsble %>%
  model(stl = STL(count))

components(pkg_stl) %>%
  as_tsibble() %>%
  autoplot(count, colour="gray") +
  geom_line(aes(y=trend), colour = "#D55E00") +
  labs(
    y = "Download count",
    title = "Daily download count for all of R-packages"
  ) +
  theme(panel.grid.major = element_blank()) +
  theme(
  axis.text=element_text(size=10),
  axis.title=element_text(size=12,face="bold"),
  plot.title = element_text(h = 0.5)
  )

```

Figure \@ref(fig:weekend-vs-weekday) shows the distributions and the median of the downloads between weekday and weekends, which differ from each other a lot. The violin plots of weekends are wider and shorter, while those of weekdays are thinner and higher, on the contrary. That is because the total downloads on weekends are less than those in weekdays. In 2012, the median and interquartile range of download logs are not very distinguished between weekdays and weekends, for the data volume was not adequate at this time as mentioned before. But after 2013, the gap between the two has been becoming more and more obvious. The median downloads of working days are significantly higher than those of weekends, and the overall download volume is also significantly larger than that of weekends as well. Interestingly, the lower adjacent sometimes occurs on weekends, such as in year 2014, 2015, 2018, 2019 and 2021, while sometimes also in weekdays, such as in year 2012, 2013, 2016, 2017 and 2020.

(ref:weekend-vs-weekday) The violin plot for downloads of all of R-packages on CRAN, between weekday and weekends.

```{r weekend-vs-weekday,fig.cap="(ref:weekend-vs-weekday)", fig.height = 7}
total_downloads_fix %>% 
  ggplot(aes(weekend, count/1e6)) +
  geom_violin() +
  geom_boxplot(width = 0.1)  +
  labs(color = "Year",
       x = "Weekday or Weekend",
       y = "Download count (in millions)") +
  facet_wrap(~year, scales = "free_y", nrow = 2) +
  scale_x_discrete(labels = c("Day", "End")) 
```


```{block, type="discovery", echo = TRUE}
**Finding 4**: Top 10% downloaded R-packages share nearly 90% cumulative download counts of the whole.
```

From the previous analysis, we could see that the cumulative download counts of R-packages show an increasing trend. It would be perfect equality if every R-package had the same download count : the last 20% downloaded R-packages would gain 20% of the total download count or the top 60% downloaded R-packages would get 60% of the total download count. But knowing from experience, we know that is hardly possible. So, here, we introduced Lorenz curve[@lorenz] to show the respective numbers of R-packages within different download levels (groups defined by quantiles of download counts). In this way, we could figure out how many download counts contributed by different downloaded R-packages.

```{r totalpkg}
#get all the packages from CRAN 
cran_names <- rownames(available:::available_packages(repos = available:::default_cran_repos)) %>%
  as.data.frame() 

colnames(cran_names)[1] <- "package"

#slice into small samples to speed up the execution
cran_names1 <- cran_names %>% 
  slice(1:850) 

cran_names2 <- cran_names %>% 
  slice(851:1701)

cran_names3 <- cran_names %>% 
  slice(1702:2552)

cran_names4 <- cran_names %>% 
  slice(2553:3403)

cran_names5 <- cran_names %>% 
  slice(3404:4254)

cran_names6 <- cran_names %>% 
  slice(4255:5105)

cran_names7 <- cran_names %>% 
  slice(5106:5956)

cran_names8 <- cran_names %>% 
  slice(5957:6807)

cran_names9 <- cran_names %>% 
  slice(6808:7657)

cran_names10 <- cran_names %>% 
  slice(7658:8508)

cran_names11 <- cran_names %>% 
  slice(8509:9359)

cran_names12 <- cran_names %>% 
  slice(9360:10210)

cran_names13 <- cran_names %>% 
  slice(10211:11061)

cran_names14 <- cran_names %>% 
  slice(11062:11912)

cran_names15 <- cran_names %>% 
  slice(11913:12763)

cran_names16 <- cran_names %>% 
  slice(12764:13614)

cran_names17 <- cran_names %>% 
  slice(13615:14465)

cran_names18 <- cran_names %>% 
  slice(14466:15316)

cran_names19 <- cran_names %>% 
  slice(15317:16167)

cran_names20 <- cran_names %>% 
  slice(16168:17018)

#although slice too much, this is also reproducible :D
cran_names21 <- cran_names %>% 
  slice(17019:length(cran_names$package))

td_start <- Sys.Date() - 182
td_end <- Sys.Date() - 2

#get total downloads for slice1
cran_names1 <- map_dfr(cran_names1, ~{
  pkgs <- cran_names1$package
  
  cran_downloads(pkgs, from = td_start, to = td_end) 
})

cran_names1 <- cran_names1 %>%
  group_by(package) %>%
  summarise(total = sum(count))

#get total downloads for slice2
cran_names2 <- map_dfr(cran_names2, ~{
  pkgs <- cran_names2$package
  
  cran_downloads(pkgs, from = td_start, to = td_end) 
})

cran_names2 <- cran_names2 %>%
  group_by(package) %>%
  summarise(total = sum(count))

#get total downloads for slice3
cran_names3 <- map_dfr(cran_names3, ~{
  pkgs <- cran_names3$package
  
  cran_downloads(pkgs, from = td_start, to = td_end) 
})

cran_names3 <- cran_names3 %>%
  group_by(package) %>%
  summarise(total = sum(count))

#get total downloads for slice4
cran_names4 <- map_dfr(cran_names4, ~{
  pkgs <- cran_names4$package
  
  cran_downloads(pkgs, from = td_start, to = td_end) 
})

cran_names4 <- cran_names4 %>%
  group_by(package) %>%
  summarise(total = sum(count))

#get total downloads for slice5
cran_names5 <- map_dfr(cran_names5, ~{
  pkgs <- cran_names5$package
  
  cran_downloads(pkgs, from = td_start, to = td_end) 
})

cran_names5 <- cran_names5 %>%
  group_by(package) %>%
  summarise(total = sum(count))

#get total downloads for slice6
cran_names6 <- map_dfr(cran_names6, ~{
  pkgs <- cran_names6$package
  
  cran_downloads(pkgs, from = td_start, to = td_end) 
})

cran_names6 <- cran_names6 %>%
  group_by(package) %>%
  summarise(total = sum(count))

#get total downloads for slice7
cran_names7 <- map_dfr(cran_names7, ~{
  pkgs <- cran_names7$package
  
  cran_downloads(pkgs, from = td_start, to = td_end) 
})

cran_names7 <- cran_names7 %>%
  group_by(package) %>%
  summarise(total = sum(count))

#get total downloads for slice8
cran_names8 <- map_dfr(cran_names8, ~{
  pkgs <- cran_names8$package
  
  cran_downloads(pkgs, from = td_start, to = td_end) 
})

cran_names8 <- cran_names8 %>%
  group_by(package) %>%
  summarise(total = sum(count))

#get total downloads for slice9
cran_names9 <- map_dfr(cran_names9, ~{
  pkgs <- cran_names9$package
  
  cran_downloads(pkgs, from = td_start, to = td_end) 
})

cran_names9 <- cran_names9 %>%
  group_by(package) %>%
  summarise(total = sum(count))

#get total downloads for slice10
cran_names10 <- map_dfr(cran_names10, ~{
  pkgs <- cran_names10$package
  
  cran_downloads(pkgs, from = td_start, to = td_end) 
})

cran_names10 <- cran_names10 %>%
  group_by(package) %>%
  summarise(total = sum(count))

#get total downloads for slice11
cran_names11 <- map_dfr(cran_names11, ~{
  pkgs <- cran_names11$package
  
  cran_downloads(pkgs, from = td_start, to = td_end) 
})

cran_names11 <- cran_names11 %>%
  group_by(package) %>%
  summarise(total = sum(count))

#get total downloads for slice12
cran_names12 <- map_dfr(cran_names12, ~{
  pkgs <- cran_names12$package
  
  cran_downloads(pkgs, from = td_start, to = td_end) 
})

cran_names12 <- cran_names12 %>%
  group_by(package) %>%
  summarise(total = sum(count))

#get total downloads for slice13
cran_names13 <- map_dfr(cran_names13, ~{
  pkgs <- cran_names13$package
  
  cran_downloads(pkgs, from = td_start, to = td_end) 
})

cran_names13 <- cran_names13 %>%
  group_by(package) %>%
  summarise(total = sum(count))

#get total downloads for slice14
cran_names14 <- map_dfr(cran_names14, ~{
  pkgs <- cran_names14$package
  
  cran_downloads(pkgs, from = td_start, to = td_end) 
})

cran_names14 <- cran_names14 %>%
  group_by(package) %>%
  summarise(total = sum(count))

#get total downloads for slice15
cran_names15 <- map_dfr(cran_names15, ~{
  pkgs <- cran_names15$package
  
  cran_downloads(pkgs, from = td_start, to = td_end) 
})

cran_names15 <- cran_names15 %>%
  group_by(package) %>%
  summarise(total = sum(count))

#get total downloads for slice16
cran_names16 <- map_dfr(cran_names16, ~{
  pkgs <- cran_names16$package
  
  cran_downloads(pkgs, from = td_start, to = td_end) 
})

cran_names16 <- cran_names16 %>%
  group_by(package) %>%
  summarise(total = sum(count))

#get total downloads for slice17
cran_names17 <- map_dfr(cran_names17, ~{
  pkgs <- cran_names17$package
  
  cran_downloads(pkgs, from = td_start, to = td_end) 
})

cran_names17 <- cran_names17 %>%
  group_by(package) %>%
  summarise(total = sum(count))

#get total downloads for slice18
cran_names18 <- map_dfr(cran_names18, ~{
  pkgs <- cran_names18$package
  
  cran_downloads(pkgs, from = td_start, to = td_end) 
})

cran_names18 <- cran_names18 %>%
  group_by(package) %>%
  summarise(total = sum(count))

#get total downloads for slice19
cran_names19 <- map_dfr(cran_names19, ~{
  pkgs <- cran_names19$package
  
  cran_downloads(pkgs, from = td_start, to = td_end) 
})

cran_names19 <- cran_names19 %>%
  group_by(package) %>%
  summarise(total = sum(count))

#get total downloads for slice20
cran_names20 <- map_dfr(cran_names20, ~{
  pkgs <- cran_names20$package
  
  cran_downloads(pkgs, from = td_start, to = td_end) 
})

cran_names20 <- cran_names20 %>%
  group_by(package) %>%
  summarise(total = sum(count))

#get total downloads for slice21
cran_names21 <- map_dfr(cran_names21, ~{
  pkgs <- cran_names21$package
  
  cran_downloads(pkgs, from = td_start, to = td_end) 
})

cran_names21 <- cran_names21 %>%
  group_by(package) %>%
  summarise(total = sum(count))


cran_names_download <- rbind(cran_names1,cran_names2,cran_names3,cran_names4,cran_names5,cran_names6,cran_names7,cran_names8,cran_names9,cran_names10,cran_names11,cran_names12,cran_names13,cran_names14,cran_names15,cran_names16,cran_names17,cran_names18,cran_names19,cran_names20,cran_names21)
```


Figure \@ref(fig:lorenz-all) shows cumulative download counts against each downloaded group. It can be seen that most of the download counts come from the top 10% downloaded R-packages. At the same time, we could also observe that the Gini value is close to 1, which indicates that the download volumes across groups are quite unbalanced. In fact, the download volume of the top 10% group is extremely distinguished from that of the following groups. It's not hard to understand that this group should contain some R-packages with high popularity and large quantities of users. 

(ref:lorenz-all) Percentiles of the download counts against cumulative download counts for R-packages at or below that percentile.

```{r lorenz-all, fig.cap="(ref:lorenz-all)",cache = TRUE}
lorenz_curve <- ggplot(cran_names_download, aes(total)) +
stat_lorenz() +
geom_abline(linetype = "dashed") +
annotate_ineq(cran_names_download$total)+
theme_bw()+
  labs(
    y = "Cumulative share of download counts",
    x = "Download quantile",
    title = "The number of R-packages occupied by each group",
    subtitle = "based on download count quantile"
  ) +
  theme(panel.grid.major = element_blank()) +
  theme(
  axis.text=element_text(size=10),
  axis.title=element_text(size=12,face="bold"),
  plot.title = element_text(h = 0.5),
  plot.subtitle = element_text(h = 0.5)
  )

lorenz_curve
```

For example, if we extracted the first 10 packages of this group in Table \@ref(tab:top10), we could find that there are many quite famous and frequently-used R-packages, such as `rlang` and `dplyr`.

```{r top10}
#quantile(cran_names_download$total,probs = seq(0, 1, 0.1)) 
cran_names_download %>%
  filter(total > 24310) %>%
  arrange(desc(total))%>%
  head(10) %>%
  kable(caption = "First 10 R-packages of top 10% downloaded group") %>%
  kable_styling(full_width = FALSE) 
```

