## Daily downloads of R

In this section, we studied the daily downloads of R language itself from `r dd_start` to `r dd_end`. The data was obtained from the `cranlogs` package [@cranlogs] as well.

```{r vars-R-downloads, cache = TRUE}
R_downloads <- cran_downloads("R", from = dd_start, to = dd_end) %>% 
  mutate(year = year(date),
         day = yday(date),
         weekend = is_weekend(date)) 
```

```{block, type="discovery", echo = TRUE}
**Finding 1**: The number of downloads shows an upward trend over time, and the variance also increases with the downloads.
```

Figure \@ref(fig:R-download-trend) shows the download trend of R on CRAN over time. It shows an upward trend over time, and the variance also increases with the download count, which indicates the volatility of the data is increasing as well. And that is resulted from the pump of R users. As for the significant spikes, it is probably quite similar to the situation of R packages, which is due to repeated downloads, weekly calendar effect and server test.

(ref:R-download-trend) The download trend of R on CRAN over time. 

```{r R-download-trend, fig.cap="(ref:R-download-trend)"}
R_downloads %>% 
  group_by(date) %>% 
  mutate(date = as.Date(date)) %>%
  summarise(total = sum(count)) %>% 
  ggplot(aes(date, total)) +
  geom_line(colour="gray")+
  labs(
    y = "Download count",
    title = "Daily total download count of R"
  )+
  theme(panel.grid.major = element_blank()) +
  theme(
  axis.text=element_text(size=10),
  axis.title=element_text(size=12,face="bold"),
  plot.title = element_text(h = 0.5)
  )
```


```{block, type="discovery", echo = TRUE}
**Finding 2**: The most used operation system for R users is Windows OS.
```

Figure \@ref(fig:R-download-trend-os) shows the comparison of operation system for R users. The number of Windows users ranks first, followed by MacOS and SRC. For Microsoft has traditionally dominated the desktop and laptop market. And Microsoft officially claims there are 400 million active users of Windows 10 itself, while Apple revealed that there are now nearly 100 million active Mac users.[@warren2017]

(ref:R-download-trend-os) The download trend of R on CRAN over time. 

```{r R-download-trend-os, fig.cap="(ref:R-download-trend-os)"}
R_downloads %>% 
  group_by(os, date) %>% 
  summarise(total = sum(count)) %>% 
  ggplot(aes(date, total, color = os)) +
  geom_line() +
  labs(
    y = "Download count",
    title = "Daily total download count of R",
    subtitle = "for different OS"
  )+
  theme(panel.grid.major = element_blank()) +
  theme(
  axis.text=element_text(size=10),
  axis.title=element_text(size=12,face="bold"),
  plot.title = element_text(h = 0.5),
  plot.subtitle = element_text(h = 0.5)
  )

```

```{block, type="discovery", echo = TRUE}
**Finding 3**: The most popular version of R is 3.2.1
```

```{r latest-version}
# replace the "latest" with the specific version
R_downloads$version[which(R_downloads$version == "latest" & R_downloads$date < "2015-03-09")] <- "3.1.2"
R_downloads$version[which(R_downloads$version == "latest" & R_downloads$date < "2015-04-16")] <- "3.1.3"
R_downloads$version[which(R_downloads$version == "latest" & R_downloads$date < "2015-06-18")] <- "3.2.0"
R_downloads$version[which(R_downloads$version == "latest" & R_downloads$date < "2015-08-14")] <- "3.2.1"
R_downloads$version[which(R_downloads$version == "latest" & R_downloads$date < "2015-12-10")] <- "3.2.2"
R_downloads$version[which(R_downloads$version == "latest" & R_downloads$date < "2016-03-30")] <- "3.2.3"
R_downloads$version[which(R_downloads$version == "latest" & R_downloads$date < "2016-03-16")] <- "3.2.4"
R_downloads$version[which(R_downloads$version == "latest" & R_downloads$date < "2016-04-14")] <- "3.2.4-revised"
R_downloads$version[which(R_downloads$version == "latest" & R_downloads$date < "2016-05-03")] <- "3.2.5"
R_downloads$version[which(R_downloads$version == "latest" & R_downloads$date < "2016-06-21")] <- "3.3.0"
R_downloads$version[which(R_downloads$version == "latest" & R_downloads$date < "2016-10-31")] <- "3.3.1"
R_downloads$version[which(R_downloads$version == "latest" & R_downloads$date < "2017-03-06")] <- "3.3.2"
R_downloads$version[which(R_downloads$version == "latest" & R_downloads$date < "2017-04-21")] <- "3.3.3"
R_downloads$version[which(R_downloads$version == "latest" & R_downloads$date < "2017-06-30")] <- "3.4.0"
R_downloads$version[which(R_downloads$version == "latest" & R_downloads$date < "2017-09-28")] <- "3.4.1"
R_downloads$version[which(R_downloads$version == "latest" & R_downloads$date < "2017-11-30")] <- "3.4.2"
R_downloads$version[which(R_downloads$version == "latest" & R_downloads$date < "2018-03-15")] <- "3.4.3"
R_downloads$version[which(R_downloads$version == "latest" & R_downloads$date < "2018-04-23")] <- "3.4.4"
R_downloads$version[which(R_downloads$version == "latest" & R_downloads$date < "2018-07-02")] <- "3.5.0"
R_downloads$version[which(R_downloads$version == "latest" & R_downloads$date < "2018-12-20")] <- "3.5.1"
R_downloads$version[which(R_downloads$version == "latest" & R_downloads$date < "2019-03-11")] <- "3.5.2"
R_downloads$version[which(R_downloads$version == "latest" & R_downloads$date < "2019-04-26")] <- "3.5.3"
R_downloads$version[which(R_downloads$version == "latest" & R_downloads$date < "2019-07-05")] <- "3.6.0"
R_downloads$version[which(R_downloads$version == "latest" & R_downloads$date < "2019-12-12")] <- "3.6.1"
R_downloads$version[which(R_downloads$version == "latest" & R_downloads$date < "2020-02-29")] <- "3.6.2"
R_downloads$version[which(R_downloads$version == "latest" & R_downloads$date < "2020-04-24")] <- "3.6.3"
R_downloads$version[which(R_downloads$version == "latest" & R_downloads$date < "2020-06-06")] <- "4.0.0"
R_downloads$version[which(R_downloads$version == "latest" & R_downloads$date < "2020-10-10")] <- "4.0.1"
R_downloads$version[which(R_downloads$version == "latest" & R_downloads$date < "2021-02-15")] <- "4.0.3"
R_downloads$version[which(R_downloads$version == "latest" & R_downloads$date < "2021-03-31")] <- "4.0.4"
R_downloads$version[which(R_downloads$version == "latest" & R_downloads$date >= "2021-03-31")] <- "4.0.5"
```

```{r R-downloadversion}
R_version <- R_downloads %>% 
  pull(version) %>%
  as.data.frame()

colnames(R_version)[1] <- "R_version"

R_version <- R_version %>%
  count(R_version) %>%
  arrange(desc(n)) %>%
  rename(count = n) 
```

And Table \@ref(tab:R-download-trend-version) shows the number of downloads of different versions of R. The most downloaded one is `r R_version$R_version[1]` with `r R_version$count[1]` times, followed by `r R_version$R_version[2]` with `r R_version$count[2]` times and `r R_version$R_version[3]` with `r R_version$count[3]` times. So, most users tend to install the latest version of R to get the newest update information.

```{r R-download-trend-version}
R_version %>%
  kable(caption = "The number of downloads of different versions of R") %>%
  kable_styling(bootstrap_options = c("hover", "striped")) %>%
  scroll_box(width = "100%", height = "400px")

```

In conclusion, the daily download trend of R is quite similar to that of R packages, and they are both significantly affected by weekly calendar issue, unusual downloads from CRAN mirrors. But in general, they both tend to increase with the growing of users.
