## Daily top 15 downloaded R-packages 

In this section, we studied the top 15 downloaded R-packages from `2013-04-01` to `2021-04-01`, to see how user preferences have been changing. The data were obtained from CRAN website [http://cran.rstudio.com/web/packages/packages.rds].

We are supposed to know that some R-packages are hold by Rstudio, some are developed by core personnel or personnel closely related to R, and some are created by prolific developers[@revolutions]. And there are also parts of R-packages that are dependency packages of others, which means the increasing downloads of their "father" packages would also promote the downloads of them. For example, R-package `fable` is dependency package within R-package `fpp3`. When users install `fpp3`, `fable` would also be installed at the same time. Naturally, the numbers of downloads for those packages can probably be higher. On the one hand, the R-packages developed by those experienced developers may be more mature and completed. On the other hand, users are more inclined to use packages produced by famous authors, which can be regarded as a kind of "good use" guarantee.

However, the existence of those packages can cause the results of user preferences biased. Therefore, we decided to explore the R-packages constructed by non-special creators, and screened out four types of R-packages, namely:

- R-packages maintained by R studio
- R-packages created by authors from R core group
- R-packages created by authors from R secondary group
- R-packages created by R related authors
- R-packages created by top 20 prolific maintainers (This is resourced at @revolutions)

```{r readcran}
url <- "http://cran.rstudio.com/web/packages/packages.rds"
db <- readRDS(url(url)) %>% 
as.data.frame() %>%
  rename(package = Package)

#cran2013_04_01 <- read_csv("data/2013-04-01.csv")
#cran2014_04_01 <- read_csv("data/2014-04-01.csv")
#cran2015_04_01 <- read_csv("data/2015-04-01.csv")
#cran2016_04_01 <- read_csv("data/2016-04-01.csv")
#cran2017_04_01 <- read_csv("data/2017-04-01.csv")
#cran2018_04_01 <- read_csv("data/2018-04-01.csv")
#cran2019_04_01 <- read_csv("data/2019-04-01.csv")
#cran2020_04_01 <- read_csv("data/2020-04-01.csv")
#cran2021_04_01 <- read_csv("data/2021-04-01.csv")

#save(cran2013_04_01, file=here::here("data/cran2013_04_01.rda"))
#save(cran2014_04_01, file=here::here("data/cran2014_04_01.rda"))
#save(cran2015_04_01, file=here::here("data/cran2015_04_01.rda"))
#save(cran2016_04_01, file=here::here("data/cran2016_04_01.rda"))
#save(cran2017_04_01, file=here::here("data/cran2017_04_01.rda"))
#save(cran2018_04_01, file=here::here("data/cran2018_04_01.rda"))
#save(cran2019_04_01, file=here::here("data/cran2019_04_01.rda"))
#save(cran2020_04_01, file=here::here("data/cran2020_04_01.rda"))
#save(cran2021_04_01, file=here::here("data/cran2021_04_01.rda"))

load("data/cran2013_04_01.rda")
load("data/cran2014_04_01.rda")
load("data/cran2015_04_01.rda")
load("data/cran2016_04_01.rda")
load("data/cran2017_04_01.rda")
load("data/cran2018_04_01.rda")
load("data/cran2019_04_01.rda")
load("data/cran2020_04_01.rda")
load("data/cran2021_04_01.rda")

```

```{r filter-list}
# filter the packages maintained by R studio
pkg_rstusio <- db %>%
  filter(grepl('RStudio', Author)) %>%
  select(package) 


# filter the packages whose author is from R core group
pkg_core <- db %>%
  filter(grepl('Douglas Bates|John Chambers|Peter Dalgaard|Robert Gentleman|Kurt Hornik|Ross Ihaka|Tomas Kalibera|Michael Lawrence|Friedrich Leisch|Uwe Ligges|Thomas Lumley|Martin Maechler|Martin Morgan|Paul Murrell|Brian Ripley|Deepayan Sarkar|Duncan Temple Lang|Luke Tierney|Simon Urbanek|Martyn Plummer|', Author)) %>%
  select(package)

# filter the packages whose author is on R secondary group
pkg_secondary <- db %>%
  filter(!grepl('Guido Masarotto|Duncan Murdoch|Henrik Bengtsson|Roger Bivand|Ben Bolker|David Brahm|Vince Carey|Saikat DebRoy|Matt Dowle|Dirk Eddelbuettel|Claus Ekstrom|John Fox|Paul Gilbert|Yu Gong|Gabor Grothendieck|Frank E Harrell Jr|Peter M. Haverty|Torsten Hothorn|Robert King|Kjetil Kjernsmo|Roger Koenker|Philippe Lambert|Jan de Leeuw|Jim Lindsey|Patrick Lindsey|Catherine Loader| Gordon Maclean|Arni Magnusson|John Maindonald|David Meyer|Ei-ji Nakama|Jens Oehlschägel|Steve Oncley|Richard O’Keefe|Hubert Palme|Roger D. Peng|José C. Pinheiro|Tony Plate|Anthony Rossini| Jonathan Rougier|Petr Savicky|Günther Sawitzki|Marc Schwartz|Arun Srinivasan|Detlef Steuer|Bill Simpson|Gordon Smyth|Adrian Trapletti|Terry Therneau|Rolf Turner|Bill Venables|Gregory R. Warnes| Andreas Weingessel|Morten Welinder|James Wettenhall|Simon Wood|and Achim Zeileis', Author)) %>%
  select(package) 


# filter the packages developed by top 20 prolific maintainers
pkg_20maintainer <- db %>% 
  filter(stringr::str_detect(Author, 'Hadley Wickham|Yihui Xie|Dirk Eddelbuettel|Jeroen Ooms|Achim Zeileis|Scott Chamberlain|Gabor Csardi|Jeroen Ooms|ORPHANED|Thomas J. Leeper|Bob Rudis|Henrik Bengtsson|Kurt Hornik|Oliver Keyes|Martin Maechler|Richard Cotton|Robin K. S. Hankin|Simon Urbanek|Kirill Muller|Torsten Hothorn|Paul Gilbert') )%>%
  select(package) 


# filter the packages developed by other R studio related authors
pkg_r_related <- db %>%
  filter(stringr::str_detect(Author, 'Hadley Wickham|Yihui Xie|Gabor Csardi|Winston Chang|Andrie de Vries|Alison Presmanes Hill|Mara Averick|Cole Arendt|Daniel Falbel|Garrick Aden-Buie|Garrett Grolemund|Gary|Joe Cheng|Jennifer (Jenny) Bryan|Jim Hester|J.J. Allaire|Jonathan|Joshua Spiewak|Dan Buch|Richard Iannone|Ralf Stubner|Tyler Finethy|Melissa Barca|Kevin Ushey|Javier Luraschi|Karl Feinauer|Charles Teague|Maria Semple|adamconroy|Ricardo Andrade|Steve Nolen|Randy Lai|Jeffrey Horner|Jan Marvin Garbuszus|Justace Clutter|Josh Paulson|Mike Bessuille|Jeffrey Arnold|Paul Kaefer|Jim Hester|Dirk Schumacher|
Philipp A.|Fabian Mundt|Fabian Mundt|boB Rudis|Asher|Henrik Bengtsson|James Lamb|rich-rstudio|Andrie de Vries|Iñaki Ucar|Mark Brown|Hiroaki Yutani|Dean Attali|Matthias Mailänder|Bruno Tremblay|Ian|John Blischak|Chris von Csefalvay|Jeroen Ooms|
Daniel Gromer|Kirill Müller|Jan Gleixner|Alexander Grueneberg|Darío Hereñú|Aron Atkins|harupiko|Barret Schloerke|James Arnold|Giuseppe Casalicchio|Fredric Johansson|Curtis Kephart|reudismam|Jeff Allen|Yuri Niyazov|Sean Kross|Carl A. B. Pearson|
Peter Glerup Ericson|Diomidis Spinellis|Paul Menzel|Lincoln Mullen|Colin Gillespie|Masafumi Okada|Øystein Sørensen|Matthew Grogan|Scott Kostyshak|Marcus Kinsella|rhinopotamus|Daiki Katsuragawa|Michael Steinbaugh|Jari Karppinen|Roy Storey|Kristofer Rye|Erin|Ben Torvaney|Pol Mesalles|Sainath Adapa|Vladimir Panfilov|Christian Brueffer|Julien Barnier|') )%>%
  select(package) 

```

```{r filter-function}
# function used to do filtering
filter_list <- function(pkg){
  
  pkg <- pkg %>%
     filter(!(package %in% pkg_20maintainer$package)) %>%
     filter(!(package %in% pkg_secondary$package)) %>%
     filter(!(package %in% pkg_rstusio$package)) %>%
     filter(!(package %in% pkg_core$package)) %>%
     filter(!(package %in% pkg_r_related$package))
  
  return(pkg)
}
```


```{r filterlist}
# exclude the packages in the above three lists
cran2013_04_01_new <- filter_list(cran2013_04_01)
cran2014_04_01_new <- filter_list(cran2014_04_01)
cran2015_04_01_new <- filter_list(cran2015_04_01)
cran2016_04_01_new <- filter_list(cran2016_04_01)
cran2017_04_01_new <- filter_list(cran2017_04_01)
cran2018_04_01_new <- filter_list(cran2018_04_01)
cran2019_04_01_new <- filter_list(cran2019_04_01)
cran2020_04_01_new <- filter_list(cran2020_04_01)
cran2021_04_01_new <- filter_list(cran2021_04_01)
```


```{r crantop15-1319}
# find the top 30 downloaded packages on 04.01 from 2013 to 2021
cran2013_0401 <- cran2013_04_01_new %>%
  drop_na() %>%
  dplyr::count(package) %>%
  arrange(desc(n)) %>%
  head(15) %>%
  select(package)
  
#cran2013_1001$package <- as.vector(cran2013_1001$package) #get rid of factors

#cran2013_1001$package = factor(cran2013_1001$package,cran2013_1001$package)

cran2014_0401 <- cran2014_04_01_new %>%
  drop_na() %>%
  dplyr::count(package) %>%
  arrange(desc(n)) %>%
  head(15) %>%
  select(package)

cran2015_0401 <- cran2015_04_01_new %>%
  drop_na() %>%
  dplyr::count(package) %>%
  arrange(desc(n)) %>%
  head(15) %>%
  select(package)

cran2016_0401 <- cran2016_04_01_new %>%
  drop_na() %>%
  dplyr::count(package) %>%
  arrange(desc(n)) %>%
  head(15) %>%
  select(package)

cran2017_0401 <- cran2017_04_01_new %>%
  drop_na() %>%
  dplyr::count(package) %>%
  arrange(desc(n)) %>%
  head(15) %>%
  select(package)

cran2018_0401 <- cran2018_04_01_new %>%
  drop_na() %>%
  dplyr::count(package) %>%
  arrange(desc(n)) %>%
  head(15) %>%
  select(package)

cran2019_0401 <- cran2019_04_01_new %>%
  drop_na() %>%
  dplyr::count(package) %>%
  arrange(desc(n)) %>%
  head(15) %>%
  select(package)

cran2020_0401 <- cran2020_04_01_new %>%
  drop_na() %>%
  dplyr::count(package) %>%
  arrange(desc(n)) %>%
  head(15) %>%
  select(package)

cran2021_0401 <- cran2021_04_01_new %>%
  drop_na() %>%
  dplyr::count(package) %>%
  arrange(desc(n)) %>%
  head(15) %>%
  select(package)

```


```{r antijoin-1319}
# find out the new top 15 packages added each year
a <- anti_join(cran2014_0401,cran2013_0401) 
b <- anti_join(cran2015_0401,cran2014_0401) 
c <- anti_join(cran2016_0401,cran2015_0401) 
d <- anti_join(cran2017_0401,cran2016_0401) 
e <- anti_join(cran2018_0401,cran2017_0401) 
f <- anti_join(cran2019_0401,cran2018_0401) 
g <- anti_join(cran2020_0401,cran2019_0401) 
h <- anti_join(cran2021_0401,cran2020_0401) 

# function used to combine data with different length 
cbind_dif <- function(x = list()){
    # Find max length
    max_length <- max(unlist(lapply(x, length)))

    # Set length of each vector as
    res <- lapply(x, function(x){
        length(x) <- max_length
        return(x)
    })

    return(as.data.frame(res))
}

pkg_change <- cbind_dif(list(package14_13 = a$package, package15_14 = b$package, package16_15 = c$package, package17_16 = d$package, package18_17 = e$package, package19_18 = f$package,package20_19 = g$package,package21_20 = h$package))

pkg_change[is.na(pkg_change)] = "-"
```

```{r semijoin-1319}
a1 <- semi_join(cran2014_0401,cran2013_0401)  
b1 <- semi_join(cran2015_0401,cran2014_0401) 
c1 <- semi_join(cran2016_0401,cran2015_0401) 
d1 <- semi_join(cran2017_0401,cran2016_0401) 
e1 <- semi_join(cran2018_0401,cran2017_0401) 
f1 <- semi_join(cran2019_0401,cran2018_0401) 
g1 <- semi_join(cran2020_0401,cran2019_0401) 
h1 <- semi_join(cran2021_0401,cran2020_0401) 

pkg_remain <- cbind_dif(list(package14_13 = a1$package, package15_14 = b1$package, package16_15 = c1$package, package17_16 = d1$package, package18_17 = e1$package, package19_18 = f1$package,package20_19 = g1$package,package21_20 = h1$package))

pkg_remain[is.na(pkg_remain)] = "-"
```

After that, we generated a lorenz curve here again in Figure \@ref(fig:lorenz-filter), it can be observed that the distribution of R-packages in each download group is more equal now and the Gini value decreases as well, for the 'extreme effect' brought by highly-downloaded packages has disappeared. Thus, the user preferences could be shown more clearly. However, after filtering, the number of remaining R-packages is only 58, which is a too small-sized sample to conduct representative conclusions, we would still focus on all of R-packages on CRAN in later analysis.


(ref:lorenz-filter) Percentiles of the download counts against cumulative download counts of R-packages after filtering four types of popular and highly-downloaded packages.

```{r lorenz-filter, fig.cap="(ref:lorenz-filter)"}
cran_names_download_new <- filter_list(cran_names_download)

ggplot(cran_names_download_new, aes(total)) +
stat_lorenz() +
geom_abline(linetype = "dashed") +
annotate_ineq(cran_names_download_new$total)+
theme_bw()+
  labs(
    y = "Cumulative share of download counts",
    x = "Download quantile",
    title = "The number of R-packages occupied by each group",
    subtitle = "based on download count quantile after filtering"
  ) +
  theme(panel.grid.major = element_blank()) +
  theme(
  axis.text=element_text(size=10),
  axis.title=element_text(size=12,face="bold"),
  plot.title = element_text(h = 0.5),
  plot.subtitle = element_text(h = 0.5)
  )
```

```{block, type="discovery", echo = TRUE}
**Finding 1**: The topic of newly added R-packages come from quite different application areas, each year. 
```

Table \@ref(tab:changed-top15pkg) shows the R-packages that newly come up to the top 15 list each year, from which we can know how the user preferences have changed year by year, compared with the previous year. To be more specific :

- For 2014, `ncdf` ranks first, which is used to provide an interface to netCDF format data. 
- For 2015, the first downloaded R-package is `XLConnectJars`, related to JAVA dependency. 
- For 2016, the first downloaded R-package is `reports`, for standardising the output of R. 
- For 2017, `lava.tobit` aims to help with estimation and simulation of latent variable models.
- For 2018, the first-ranking `ReportsRs` is for creating Microsoft Word and Powerpoint documents. 
- For 2019, `CALIBERrfimpute` is used to impute missing values in analysis datasets using full conditional specifications. 
- For 2020, `SparkR` is similar to `dplyr` but for large datasets. 
- For 2021, `heatmap.plus` is an extension of `heatmap()` function.



```{r changed-top15pkg}
pkg_change %>%
  kable(caption = "Changed top 15 downloaded R-packages from 2013 to 2019") %>%
  kable_styling(bootstrap_options = c("hover", "striped")) %>%
  scroll_box(width = "100%", height = "400px")

```

```{block, type="discovery", echo = TRUE}
**Finding 2**: The topic of R-packages changes least during 2017 and 2019. The most popular application filed is on JAVA dependency.
```

Table \@ref(tab:unchanged-top15pkg) shows the R-packages that remain unchanged each year, compared to the previous year, from which we can know which packages are relatively stable in popularity.

To be more specific, packages like `XLConnectJars`, `DMwR`, `KoNLP`, and `gWidgets` are relatively popular through years from 2014 to 2021. They are used for providing JAVA dependency, data mining, linguistic research and providing API for building toolkit-independent, interactive GUIs.

```{r  unchanged-top15pkg}
pkg_remain %>%
  kable(caption = "Unchanged top 15 downloaded R-packages from 2013 to 2019") %>%
  kable_styling(bootstrap_options = c("hover", "striped")) %>%
  scroll_box(width = "100%", height = "400px")
```

Next, we changed the object to trending R-packages. Trending R-packages are ones downloaded at least 1000 times last week, which have increased significantly compared to the average weekly downloads in the previous 24 weeks[@r-hub]. That is to say, they are packages with significantly high download volume in a recent short time. Through their topics, we can know what application areas of R-packages that people are concerned about recently.

```{block, type="discovery", echo = TRUE}
**Finding 3**: The most popular topic of trending R-packages.
```

```{r taskview-function}
# to get all the topic names from CRAN task view
library(ctv)
task_topic <- available.views(repos = "https://cran.csiro.au/")

topic_name <- task_topic[[1]]$name
x <- lapply(1:length(task_topic),function(i) { topic_name[i] <- task_topic[[i]]$name})

task_topic_all <- list.rbind(x) %>%
  as.data.frame()

colnames(task_topic_all)[1] <- 'topic'


# to get all the packages from CRAN task view along with their topics
pkg_taskview_total = data.frame()

for (i in c(1:length(task_topic_all$topic))) {
  
    topic_pkg <- ctv:::.get_pkgs_from_ctv_or_repos(paste0(task_topic_all$topic[i]), 
                                              repos = "http://cran.rstudio.com/")[[1]]


   df  <- data.frame(matrix(unlist(topic_pkg), nrow=length(topic_pkg), byrow=TRUE),stringsAsFactors=FALSE) %>%
     mutate(topic = paste0(task_topic_all$topic[i]))
   
   colnames(df)[1] <-'packages'
  
   pkg_taskview_total <- rbind(pkg_taskview_total,df)
  
}

colnames(pkg_taskview_total)[1] <- 'package'

# to figure out the classification of packages according to CRAN task view
# plyr::match_df(pkg_taskview_total,c,on = "package")

```

```{r trending-topic}
# read trending packages recently
pkg_trending <- cran_trending()

pkg_trending_new <- pkg_trending %>%
  select(-score)

pkg_trending_compare <- plyr::match_df(pkg_taskview_total,pkg_trending_new,on = "package") %>%
  group_by(topic)
```

```{r trendingcount}
pkg_trendcom_count <- pkg_trending_compare %>%
  dplyr::count(topic) %>%
  rename(`download times` = n)%>%
  arrange(desc(`download times`))
```

Table \@ref(tab:trending-count) shows the top 10 downloaded topics for trending R-packages. The most popular topic is `r pkg_trendcom_count$topic[1]`, followed by `r pkg_trendcom_count$topic[2]` and `r pkg_trendcom_count$topic[3]`. This is easy to understand : the numbers of users from different fields are different, so the downloads of R-packages in different topics also varies. It seems that `r pkg_trendcom_count$topic[1]` is quite heated recently.

```{r trending-count}
pkg_trendcom_count %>%
  head(10) %>%
  kable(caption = "Ranking topics of trending R-packages") %>%
  kable_styling(bootstrap_options = c("hover", "striped"))
```

Apart from the topics of R-packages, what other factors can probably be linked to download volumes? With this question in mind, we then explored the relationship between the total number of download counts for all of CRAN R-packages and the earliest release date in the past year. We also studied the relationship between the total download volume and the number of updates, the number of commits on master (main) branch in GitHub repositories, the lengths and the alphabetical order of names, over the most recent 6 month period, in the following sections.
