---
title: "ETC5543 Presentation"
subtitle: "The evolution of R Packages"
author: "Yiwen Zhang"
supervisor: "Emi Tanaka"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: xaringan-themer.css
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
  
---
```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(echo = FALSE, 
                      cache=TRUE, 
                      message=FALSE, 
                      warning=FALSE,
                      fig.align = 'left')

library(tidyverse)
library(xaringan)
library(cranlogs)
library(glue)
library(grid)
 library(pkgsearch)
 library(ctv)
 library(lubridate)
 library(jsonlite)
 library(htmltools)
 library(httpuv)
 library(httr)
 library(kableExtra)
 library(packageRank)
 library(fpp3)
 library(slider)
 library(rvest)
 library(rlist)
 library(available)
 library(xml2)
 library(stats)
 library(gglorenz)


our_theme <- theme(rect = element_rect(fill = "#4e5a65"),
        text = element_text(color = "white", size = 10),
        panel.background = element_rect(fill = "#4e5a65"),
        axis.text = element_text(color = "white"),
        panel.border = element_rect(color = "white", size = 0.8),
        plot.title = element_text(size = 12, face = "bold", colour = "white"),
        plot.subtitle = element_text(size = 15, face = "italic", colour = "white"),
        axis.ticks = element_line(colour = "white")
        )

# Set new theme for graphs
our_theme1 <- theme(rect = element_rect(fill = "#023858"),
        text = element_text(color = "white", size = 10),
        panel.background = element_rect(fill = "#023858"),
        axis.text = element_text(color = "white"),
        panel.border = element_rect(color = "white", size = 0.8),
        plot.title = element_text(size = 12, face = "bold", colour = "white"),
        plot.subtitle = element_text(size = 15, face = "italic", colour = "white"),
        axis.ticks = element_line(colour = "white")
        )

theme_set(theme_bw(base_size = 14) +
            theme(plot.title.position = "plot"))
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)
style_duo_accent(
  primary_color = "#55B4B0",
  secondary_color = "#55B4B0",
  inverse_header_color = "#FFFFFF"
)
```

# `r emo::ji("gold")`Introduction
--

- There are over **two million** users of R

--

- There are **17700** R packages on CRAN

--

```{r trend, include=FALSE}
# to get all the topic names from CRAN task view
library(ctv)
task_topic <- available.views(repos = "https://cran.csiro.au/")

topic_name <- task_topic[[1]]$name
x <- lapply(1:length(task_topic),function(i) { topic_name[i] <- task_topic[[i]]$name})

task_topic_all <- list.rbind(x) %>%
  as.data.frame()

colnames(task_topic_all)[1] <- 'topic'


# to get all the packages from CRAN task view along with their topics
pkg_taskview_total = data.frame()

for (i in c(1:length(task_topic_all$topic))) {
  
    topic_pkg <- ctv:::.get_pkgs_from_ctv_or_repos(paste0(task_topic_all$topic[i]), 
                                              repos = "http://cran.rstudio.com/")[[1]]


   df  <- data.frame(matrix(unlist(topic_pkg), nrow=length(topic_pkg), byrow=TRUE),stringsAsFactors=FALSE) %>%
     mutate(topic = paste0(task_topic_all$topic[i]))
   
   colnames(df)[1] <-'packages'
  
   pkg_taskview_total <- rbind(pkg_taskview_total,df)
  
}

colnames(pkg_taskview_total)[1] <- 'package'

# read trending packages recently
pkg_trending <- cran_trending()

pkg_trending_new <- pkg_trending %>%
  select(-score)

pkg_trending_compare <- plyr::match_df(pkg_taskview_total,pkg_trending_new,on = "package") %>%
  group_by(topic)

pkg_trendcom_count <- pkg_trending_compare %>%
  dplyr::count(topic) %>%
  arrange(desc(n))
```

- Most recently trending package is about **`r pkg_trendcom_count$topic[1]`** 

--

## `r emo::ji("thinking")` Question :

.center[
### *How to understand the popularity of the R package?*
]

--

- understand **CRAN download counts** 

--

- explore **influential factors**

---

## `r emo::ji("gold")`The daily download of packages

.center[

```{r include=FALSE}
dd_start <- "2012-10-01"
dd_end <- Sys.Date() - 2

is_weekend <- function(date) {
  weekdays(date) %in% c("Saturday", "Sunday")
}

total_downloads <- cran_downloads(from = dd_start, to = dd_end) %>% 
  mutate(year = year(date),
         day = yday(date),
         weekend = is_weekend(date)) 
```

```{r trend-daily, fig.cap="(ref:trend)"}

total_downloads_fix <- total_downloads %>% 
  mutate(count = ifelse(count > 3e6 & year==2014 | count > 10e6 & year==2018, 
                        NA, count)) %>% #remove the unusual observations in 2014 and 2018
  group_by(year) %>% 
  mutate(max_count = max(count, na.rm = TRUE)) %>% 
  ungroup()

total_downloads_fix %>% 
  ggplot(aes(date, count/1e6)) +
  geom_line(colour="gray") +
  labs(x = "Date", y = "Download count (in millions)",title = "Daily download count of total packages") +
  theme(
  axis.text=element_text(size=10),
  axis.title=element_text(size=12,face="bold"),
  plot.title = element_text(h = 0.5)
  )
```

]


---

# `r emo::ji("thinking")` Question :

.center[
## *What do CRAN download counts mean?*
]

---

### *Finding 1* Unusual spike in 2014 and 2018

.center[

```{r unusual1418}
plot_daily <- total_downloads %>% 
  group_by(year) %>% 
  mutate(max_count = max(count)) %>% 
  ungroup() %>% 
  filter(year %in% c(2014, 2018)) %>% 
  ggplot(aes(x = day, y = count/1e6)) +
  geom_area(aes(y = weekend * max_count/1e6),
            fill="#e3e3e3")+
  geom_line() +
  labs(x = "Day",
       y = 'Download count (in millions)',
       title = "Daily download for 2014 and 2018") +
  facet_grid(facets = year ~ ., 
             scales = "free_y") +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
  plot.title = element_text(h = 0.5))

plot_daily
```

]

---

.left[
###Spike in 2014 most from

- several packages, such as 

- the *same* IP

- Indonesia

]

--

.right[
###Spike in 2018 most from

tidyverse 


Several *consecutive* IP :

a) same person

b) server issue 

US 

]

---
### *Finding 2* **10%** packages share **90%** cumulative download count

```{r totaldownload}
#get all the packages from CRAN 
cran_names <- rownames(available:::available_packages(repos = available:::default_cran_repos)) %>%
  as.data.frame() 

colnames(cran_names)[1] <- "package"

#slice into small sample to speed up the execution
cran_names1 <- cran_names %>% 
  slice(1:850) 

cran_names2 <- cran_names %>% 
  slice(851:1701)

cran_names3 <- cran_names %>% 
  slice(1702:2552)

cran_names4 <- cran_names %>% 
  slice(2553:3403)

cran_names5 <- cran_names %>% 
  slice(3404:4254)

cran_names6 <- cran_names %>% 
  slice(4255:5105)

cran_names7 <- cran_names %>% 
  slice(5106:5956)

cran_names8 <- cran_names %>% 
  slice(5957:6807)

cran_names9 <- cran_names %>% 
  slice(6808:7657)

cran_names10 <- cran_names %>% 
  slice(7658:8508)

cran_names11 <- cran_names %>% 
  slice(8509:9359)

cran_names12 <- cran_names %>% 
  slice(9360:10210)

cran_names13 <- cran_names %>% 
  slice(10211:11061)

cran_names14 <- cran_names %>% 
  slice(11062:11912)

cran_names15 <- cran_names %>% 
  slice(11913:12763)

cran_names16 <- cran_names %>% 
  slice(12764:13614)

cran_names17 <- cran_names %>% 
  slice(13615:14465)

cran_names18 <- cran_names %>% 
  slice(14466:15316)

cran_names19 <- cran_names %>% 
  slice(15317:16167)

cran_names20 <- cran_names %>% 
  slice(16168:17018)

cran_names21 <- cran_names %>% 
  slice(17019:length(cran_names$package))

td_start <- "2020-10-01"
td_end <- Sys.Date() - 2

#get total download for slice1
cran_names1 <- map_dfr(cran_names1, ~{
  pkgs <- cran_names1$package
  
  cran_downloads(pkgs, from = td_start, to = td_end) 
})

cran_names1 <- cran_names1 %>%
  group_by(package) %>%
  summarise(total = sum(count))

#get total download for slice2
cran_names2 <- map_dfr(cran_names2, ~{
  pkgs <- cran_names2$package
  
  cran_downloads(pkgs, from = td_start, to = td_end) 
})

cran_names2 <- cran_names2 %>%
  group_by(package) %>%
  summarise(total = sum(count))

#get total download for slice3
cran_names3 <- map_dfr(cran_names3, ~{
  pkgs <- cran_names3$package
  
  cran_downloads(pkgs, from = td_start, to = td_end) 
})

cran_names3 <- cran_names3 %>%
  group_by(package) %>%
  summarise(total = sum(count))

#get total download for slice4
cran_names4 <- map_dfr(cran_names4, ~{
  pkgs <- cran_names4$package
  
  cran_downloads(pkgs, from = td_start, to = td_end) 
})

cran_names4 <- cran_names4 %>%
  group_by(package) %>%
  summarise(total = sum(count))

#get total download for slice5
cran_names5 <- map_dfr(cran_names5, ~{
  pkgs <- cran_names5$package
  
  cran_downloads(pkgs, from = td_start, to = td_end) 
})

cran_names5 <- cran_names5 %>%
  group_by(package) %>%
  summarise(total = sum(count))

#get total download for slice6
cran_names6 <- map_dfr(cran_names6, ~{
  pkgs <- cran_names6$package
  
  cran_downloads(pkgs, from = td_start, to = td_end) 
})

cran_names6 <- cran_names6 %>%
  group_by(package) %>%
  summarise(total = sum(count))

#get total download for slice7
cran_names7 <- map_dfr(cran_names7, ~{
  pkgs <- cran_names7$package
  
  cran_downloads(pkgs, from = td_start, to = td_end) 
})

cran_names7 <- cran_names7 %>%
  group_by(package) %>%
  summarise(total = sum(count))

#get total download for slice8
cran_names8 <- map_dfr(cran_names8, ~{
  pkgs <- cran_names8$package
  
  cran_downloads(pkgs, from = td_start, to = td_end) 
})

cran_names8 <- cran_names8 %>%
  group_by(package) %>%
  summarise(total = sum(count))

#get total download for slice9
cran_names9 <- map_dfr(cran_names9, ~{
  pkgs <- cran_names9$package
  
  cran_downloads(pkgs, from = td_start, to = td_end) 
})

cran_names9 <- cran_names9 %>%
  group_by(package) %>%
  summarise(total = sum(count))

#get total download for slice10
cran_names10 <- map_dfr(cran_names10, ~{
  pkgs <- cran_names10$package
  
  cran_downloads(pkgs, from = td_start, to = td_end) 
})

cran_names10 <- cran_names10 %>%
  group_by(package) %>%
  summarise(total = sum(count))

#get total download for slice11
cran_names11 <- map_dfr(cran_names11, ~{
  pkgs <- cran_names11$package
  
  cran_downloads(pkgs, from = td_start, to = td_end) 
})

cran_names11 <- cran_names11 %>%
  group_by(package) %>%
  summarise(total = sum(count))

#get total download for slice12
cran_names12 <- map_dfr(cran_names12, ~{
  pkgs <- cran_names12$package
  
  cran_downloads(pkgs, from = td_start, to = td_end) 
})

cran_names12 <- cran_names12 %>%
  group_by(package) %>%
  summarise(total = sum(count))

#get total download for slice13
cran_names13 <- map_dfr(cran_names13, ~{
  pkgs <- cran_names13$package
  
  cran_downloads(pkgs, from = td_start, to = td_end) 
})

cran_names13 <- cran_names13 %>%
  group_by(package) %>%
  summarise(total = sum(count))

#get total download for slice14
cran_names14 <- map_dfr(cran_names14, ~{
  pkgs <- cran_names14$package
  
  cran_downloads(pkgs, from = td_start, to = td_end) 
})

cran_names14 <- cran_names14 %>%
  group_by(package) %>%
  summarise(total = sum(count))

#get total download for slice15
cran_names15 <- map_dfr(cran_names15, ~{
  pkgs <- cran_names15$package
  
  cran_downloads(pkgs, from = td_start, to = td_end) 
})

cran_names15 <- cran_names15 %>%
  group_by(package) %>%
  summarise(total = sum(count))

#get total download for slice16
cran_names16 <- map_dfr(cran_names16, ~{
  pkgs <- cran_names16$package
  
  cran_downloads(pkgs, from = td_start, to = td_end) 
})

cran_names16 <- cran_names16 %>%
  group_by(package) %>%
  summarise(total = sum(count))

#get total download for slice17
cran_names17 <- map_dfr(cran_names17, ~{
  pkgs <- cran_names17$package
  
  cran_downloads(pkgs, from = td_start, to = td_end) 
})

cran_names17 <- cran_names17 %>%
  group_by(package) %>%
  summarise(total = sum(count))

#get total download for slice18
cran_names18 <- map_dfr(cran_names18, ~{
  pkgs <- cran_names18$package
  
  cran_downloads(pkgs, from = td_start, to = td_end) 
})

cran_names18 <- cran_names18 %>%
  group_by(package) %>%
  summarise(total = sum(count))

#get total download for slice19
cran_names19 <- map_dfr(cran_names19, ~{
  pkgs <- cran_names19$package
  
  cran_downloads(pkgs, from = td_start, to = td_end) 
})

cran_names19 <- cran_names19 %>%
  group_by(package) %>%
  summarise(total = sum(count))

#get total download for slice20
cran_names20 <- map_dfr(cran_names20, ~{
  pkgs <- cran_names20$package
  
  cran_downloads(pkgs, from = td_start, to = td_end) 
})

cran_names20 <- cran_names20 %>%
  group_by(package) %>%
  summarise(total = sum(count))

#get total download for slice21
cran_names21 <- map_dfr(cran_names21, ~{
  pkgs <- cran_names21$package
  
  cran_downloads(pkgs, from = td_start, to = td_end) 
})

cran_names21 <- cran_names21 %>%
  group_by(package) %>%
  summarise(total = sum(count))


cran_names_download <- rbind(cran_names1,cran_names2,cran_names3,cran_names4,cran_names5,cran_names6,cran_names7,cran_names8,cran_names9,cran_names10,cran_names11,cran_names12,cran_names13,cran_names14,cran_names15,cran_names16,cran_names17,cran_names18,cran_names19,cran_names20,cran_names21)
```


```{r lorenz}
lorenz_curve <- ggplot(cran_names_download, aes(total)) +
stat_lorenz() +
geom_abline(linetype = "dashed") +
annotate_ineq(cran_names_download$total)+
theme_bw()+
  labs(
    y = "Cumulative share of download count",
    x = "Download quantile",
    title = "The number of packages occupied by each group",
    subtitle = "based on download count quantile"
  ) +
  theme(panel.grid.major = element_blank()) +
  theme(
  axis.text=element_text(size=10),
  axis.title=element_text(size=12,face="bold"),
  plot.title = element_text(h = 0.5),
  plot.subtitle = element_text(h = 0.5)
  )

lorenz_curve
```

---

### Other interesting findings for R

- The **most used** operation system is **Windows**

--

- The **most popular** version is **3.2.1**

--


- The most stably popular packages during 2017 to 2019 is about **JAVA dependency**

---
# `r emo::ji("thinking")` Question :

.center[
## *What would affect the download counts?*
]

--

- initial release date

--

- the number of commits on Github repository

--

- update times

---
# `r emo::ji("gold")`The initial release date

--

## CRAN task view packages

--

### Packages that are initially released earlier on CRAN tend to have a higher download count in the past year.

---

.center[
### `r emo::ji("gold")`Initial release date VS total download count
]

```{r readtaskview,include=FALSE}
load("data/taskview_downloads.rda")
load("data/pkg_releases.rda")
```

.center[
```{r release-downloads}
initial_release <- pkg_releases %>% 
  mutate(releases = as.Date(release)) %>% 
  group_by(package) %>% 
  summarise(initial = min(releases)) %>% 
  ungroup()

taskview_downloads %>% 
  group_by(package) %>% 
  summarise(total = sum(count), 
            taskview = unique(taskview)) %>% 
  left_join(initial_release, by = "package") %>% 
  ggplot(aes(initial, total,colour = taskview)) +
  geom_point() +
  geom_smooth() +
  facet_wrap(~taskview, ncol = 1) +
  scale_y_log10() +
  labs(x = "Initial release date",
       y = "Download counts") +
  theme(panel.grid.major = element_blank()) +
  theme(
  axis.text=element_text(size=10),
  axis.title=element_text(size=12,face="bold"),
  plot.title = element_text(h = 0.5),
  plot.subtitle = element_text(h = 0.5)
  )
```
]

---
### `r emo::ji("gold")`Compare between fable and forecast

```{r compare-fable-forecast}
lh_dt_start <- "2020-10-01" #last half year
lh_dt_end <- Sys.Date() - 2

# transform the daily download of 'fable' to time series table
fable <- cran_downloads(package = "fable",from = lh_dt_start, to = lh_dt_end)
forecast <- cran_downloads(package = "forecast",from = lh_dt_start, to = lh_dt_end)

fable <- fable %>%
  as_tsibble(index = date) 

forecast <- forecast %>%
  as_tsibble(index = date) 
```

```{r ma-plot}
# use 7 MA can get a equal weighed 7 MA 
fable_ma <- fable %>%
  mutate(
    `7-MA` = slider::slide_dbl(count, mean,
                .before = 3, .after = 3, .complete = TRUE)
    )

colors <- c('fable' = '#D55E00', 'forecast' = 'violetred4')

p_fbl <- fable_ma %>%
  autoplot(count, color = "gray") +
  geom_line(aes(y = `7-MA`,colour = 'fable')) +
  geom_vline(xintercept = as.numeric(ymd("2021-01-29")), linetype="dashed", #to get geom_vline to an x-axis of class date
                color = "violetred4", size=0.8) +
  labs( 
  title = "Weighed moving average of fable and forecast",
  subtitle = "from 2020-12-03 up to now") +
  theme_minimal()  +
  theme(panel.grid.major = element_blank()) +
  theme(
  axis.text=element_text(size=10),
  axis.title.x=element_blank(),
  axis.title=element_text(size=12,face="bold"),
  plot.title = element_text(h = 0.5),
  plot.subtitle = element_text(h = 0.5)) 

forecast_ma <- forecast %>%
  mutate(
    `7-MA` = slider::slide_dbl(count, mean,
                .before = 3, .after = 3, .complete = TRUE)
    )

p_fcst <- forecast_ma %>%
  autoplot(count, color = "gray") +
  geom_line(aes(y = `7-MA`,colour = 'forecast')) +
  theme_minimal()  +
  theme(panel.grid.major = element_blank()) +
  theme(
  axis.text=element_text(size=10),
  axis.title=element_text(size=12,face="bold")) 


g_fbl <- ggplotGrob(p_fbl)
g_fcst <- ggplotGrob(p_fcst)
gff <- rbind(g_fbl, g_fcst, size = "first")
gff$widths <- unit.pmax(g_fbl$widths, g_fcst$widths)
grid.newpage()
grid.draw(gff)
```


---
# `r emo::ji("gold")`The number of commits on Github repo

--

## All available CRAN packages with Github repo

--

.center[
###*5769*###
]

--

### `r emo::ji("smile")`Generally, more commits, more download counts.

---

### `r emo::ji("gold")`The number of commits on Github repo

```{r commits}
load("data/pkg_commits_all.rda")

pkg_commits_all %>%
  mutate(total = as.numeric(total)) %>%
  mutate(commits = as.numeric(commits)) %>%
  ggplot(aes(x = commits, y = total)) +
  geom_point() +
  geom_smooth(se = F) +
  scale_y_log10() +
  labs( y = 'Total download count',
          x = 'The number of commits',
    title = "Commits counts against download counts",
    subtitle = "of 5769 packages for last half a year") +
    #annotate("text",y= 70000,x= 500,label="In general, more commits, more downloads.",color="red") +
  #theme_minimal()  +
  theme(panel.grid.major = element_blank()) +
  theme(
  axis.text=element_text(size=10),
  axis.title=element_text(size=12,face="bold"),
  plot.title = element_text(h = 0.5),
  plot.subtitle = element_text(h = 0.5))
```


---

# `r emo::ji("gold")`The update times

--

## All available CRAN packages

--

### Download count *slightly* rise with the update times

--

### Keep updating really matters

---

### `r emo::ji("gold")`The update times

[need add figure here]

---
# `r emo::ji("gold")`Name Analysis

##`r emo::ji("thinking")` **name length**

##`r emo::ji("thinking")` **alphabetical name order**

---
### `r emo::ji("thinking")`Over half of the packages tend to have shorter names

```{r name-length, include=FALSE}
cran_namelth_download <- cran_names_download %>%
  mutate(length_name = nchar(package)) %>%
  rowwise()%>%
  mutate(length_name = as.numeric(length_name)) 


cran_namelth_download <- cran_namelth_download %>%
  arrange(desc(total)) 

`total average name length`  <- as.numeric(mean(cran_namelth_download$length_name))
`pkg_trending_total` <- as.numeric(length(cran_namelth_download$package))

cran_namelth_download1 <- cran_namelth_download %>%
  group_by(package) %>%
  dplyr::filter(length_name < `total average name length`) %>%
  ungroup() %>%
  dplyr::summarise(`number of short names` = length(package)) %>%
  mutate(`percentage of short names` = (`number of short names`/pkg_trending_total)*100)

compare_all_namelth <- cbind(cran_namelth_download1,`total average name length`)

```

```{r}
compare_all_namelth %>%
  kable(caption = "Percentage of packages whose updates are less than average") %>%
  kable_styling(bootstrap_options = c("hover", "striped"))
```

--

### `r emo::ji("smile")`Probably, shorter names are easier to be remembered by users !

---

### `r emo::ji("wink")` life experience : name of novel book

[add pics for same type of novels but with different name length and published date]

---

### `r emo::ji("thinking")` For all packages on CRAN, the average name length tends to generally increase each year.

[need a figure here]

---

### `r emo::ji("thinking")` The difference in downloads for each alphabetical groups varies little

```{r}

```

---

# `r emo::ji("heart")`Acknowledgements


---

# `r emo::ji("gold")`References